---
title: "R Tutorial 1"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Base R Syntax and Tidyverse
### Base R

Write the R code required to create a numeric vector called `x`:
```{r vectorn, exercise=TRUE}

```

Write the R code required to create a factor vector called `y`:
```{r vectorf, exercise=TRUE}

```

Write the R code required to create a data frame built of `x` and `y` called `df`:
```{r df1, exercise=TRUE}

```


### Importing Your Data

You have data that is comma delimited called `yourdata.csv`. Write the R code necessary to important that data.
```{r import1, exercise=TRUE}

```

Fill in the following missing pieces to make import an SPSS file. [Do Not Run Code]
```{r add-function, exercise=TRUE, exercise.lines = 4}
library( )
df <- read ("yourdata.sav")
```

### Quick Summaries

```{r quiz1}
quiz(
  question("Which function(s) can give you a summary of your entire data frame?",
    answer("factor()"),
    answer("table1()", correct = TRUE),
    answer("summary()", correct = TRUE),
    answer("table()"),
    answer("No such functions exist!")
  )
)
```

Use the three step summary to assess the mean of `y` grouped by `x` in the data frame `df`.
```{r threestep, exercise=TRUE, exercise.eval=TRUE}
df <- data.frame(
  "x" = c(0,0,0,0,0,1,1,1,1,1),
  "y" = c(0,1,3,1,4,2,3,4,2,3)
)


```

```{r threestep-hint}
df <- data.frame(
  "x" = c(0,0,0,0,0,1,1,1,1,1),
  "y" = c(0,1,3,1,4,2,3,4,2,3)
)

df %>%
  group_by() %>%
  summarize()
```


## Reshaping and Other Cleaning

### Reshaping
```{r quiz2}
quiz(
  question("Which function(s) can take your data from wide format to long format?",
    answer("reshape()", correct = TRUE),
    answer("gather()", correct = TRUE),
    answer("spread()"),
    answer("long()", correct = TRUE)
  )
)
```

Reshape the following wide form data frame to a long form.
```{r reshape1, exercise=TRUE, exercise.eval=TRUE}
df_wide <- data.frame(
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)


```

```{r reshape1-hint}
df_wide <- data.frame(
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)

df_long <- long(df_wide,
                c(),
                v.names = )
```

### Cleaning

Change all 999's to NA in the data frame. The data frame has five variables---`x`, `y`, `z`, `a`, and `b`. Use a loop.
```{r toNA, exercise=TRUE, exercise.lines = 4, exercise.eval=TRUE}

```
```{r toNA-hint}
library(furniture)
df[] = lapply(df )
```

Change all `NaN`'s to NA in the data frame. Again, the data frame has five variables---`x`, `y`, `z`, `a`, and `b`. Use a loop.
```{r toNA2, exercise=TRUE, exercise.lines = 4, exercise.eval=TRUE}

```
```{r toNA2-hint}
library(furniture)
df[] = lapply(df )
```

### Joining
Write the R code necessary to join `df1` and `df2` by variable `ID`. We want to keep all those in `df1`.
```{r joining1, exercise=TRUE}

```

### Mutating

Add a variable called `z` to `df` that is equal to `1` if `x` is greater than `10`, `0` if `x` is less than or equal to `10`, and `NA` otherwise.
```{r mutate1, exercise=TRUE, exercise.lines = 4}
df_wide <- data.frame(
  "x" = c(10,7,13,11,4,12,9,4,8,3),
  "y" = c(2,1,3,2,4,3,5,2,3,1)
)


```

### Selecting and Filtering

We only want to keep individuals with a depression score (`dep`) greater than 10. Finish the code below to do that.
```{r select1, exercise=TRUE, exercise.lines = 4}
df2 <- df %>%
   (dep > 10)
```

```{r quiz3}
quiz(
  question("Can we select and filter in the same overall step? If so, how?",
    answer("No way. Stupid idea."),
    answer("Yes; using a pipe you can select and then filter or vice versa.", correct = TRUE),
    answer("Yes; using the function select_filter() it is easy."),
    answer("Yes; but I don't know how.")
  )
)
```


## `ggplot2`, Tables, and Output

### `ggplot2`
```{r gg1, exercise=TRUE, exercise.lines = 4}
ggplot(df, aes(x = gender, y = productivity_mean, color = gender)) +
  geom_bar(stat = "identity") +
  theme_classic() +
  scale_color_manual(values = c("dodgerblue", "coral"))
```

```{r quiz4}
quiz(
  question("What kind of plot do you expect from the previous ggplot code?",
    answer("A blank plot."),
    answer("A histogram showing the frequencies of each gender."),
    answer("No. Just no."),
    answer("A bar plot showing the mean of productivity for each gender.", correct = TRUE)
  ),
  question("What colors do you expect to see on the plot?",
    answer("It's a colorless world so I expect no colors to be present."),
    answer("The bars will be outlined in blue or coral.", correct = TRUE),
    answer("The bars will be filled in with blue or coral."),
    answer("The bars will be filled in and outlined with blue or coral.")
  ),
  question("Why did it use `stat = 'identity'`?",
    answer("To trick me."),
    answer("It makes it so the plot is a bar plot instead of a histogram.", correct = TRUE),
    answer("It is actually unnecessary since it is the default."),
    answer("To remind the plot who he or she is.")
  )
)
```

We want to show the growth from time 1 to time 2 in the `y` variable and color it (group it by `id` so we have a spaghetti plot) by `x`. Fix the code to make the plot work.
```{r gg2, exercise=TRUE, exercise.lines = 9, exercise.eval=TRUE, warning=FALSE, message=FALSE}
df_wide <- data.frame(
  "id" = 1:10,
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)
library(tidyverse)
ggplot(df_wide, aes(x = y1, y = y2, group = id, color = x)) +
  geom_line()
```
```{r gg2-hint}
library(furniture)
## Reshape!!!
df_long = long(df_wide,
               c("y1", "y2"),
               v.names = "y")
## Now plot it
```

### Tables

You are given the following data frame and want to create a table of descriptives. Demonstrate how you would obtain this table?
```{r tab1, exercise=TRUE, exercise.lines = 8, exercise.eval=TRUE, warning=FALSE, message=FALSE}
df_wide <- data.frame(
  "id" = 1:10,
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)
```

Using the tidyverse framework, show the "three step summary" on the following data frame.
```{r tab1, exercise=TRUE, exercise.lines = 8, exercise.eval=TRUE, warning=FALSE, message=FALSE}
df_wide <- data.frame(
  "id" = 1:10,
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)
```


