---
title: "R Tutorial 2"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = FALSE)
```

## Functions and Loops
### Base R

First, write a function that can be looped. Note, that generally means the function works on a single vector.
```{r loops1, exercise=TRUE, exercise.lines = 5, exercise.eval=TRUE, warning=FALSE, message=FALSE}


```

Now apply this function to the following data frame using `lapply()`.
```{r loops2, exercise=TRUE, exercise.lines = 8, exercise.eval=TRUE, warning=FALSE, message=FALSE}
df <- data.frame(
  "id" = 1:10,
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)


```

Write a function that assesses how many levels a variable has, and if it has less than 4 levels, makes it a factor. Try it out on the following data frame.
```{r loops3, exercise=TRUE, exercise.lines = 8, exercise.eval=TRUE, warning=FALSE, message=FALSE}
df <- data.frame(
  "id" = 1:10,
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)



```


### `purrr`

Using one of the `purrr` functions, find the mean of both variables--`x` and `y`.
```{r map1, exercise=TRUE, exercise.eval=TRUE}
df <- data.frame(
  "x" = c(0,0,0,0,0,1,1,1,1,1),
  "y" = c(0,1,3,1,4,2,3,4,2,3)
)


```
```{r map1-hint}
df <- data.frame(
  "x" = c(0,0,0,0,0,1,1,1,1,1),
  "y" = c(0,1,3,1,4,2,3,4,2,3)
)

df %>% 
  map()
```

If the `id` is equal to 1 or 5 make `y1` equal to `NA` using the `map()` function from `purrr`.
```{r map2, exercise=TRUE, exercise.lines = 8, exercise.eval=TRUE, warning=FALSE, message=FALSE}
df <- data.frame(
  "id" = 1:10,
  "x"  = c(0,0,0,0,0,1,1,1,1,1),
  "y1" = c(0,1,3,1,4,2,3,4,2,3),
  "y2" = c(2,1,3,2,4,3,5,2,3,1)
)



```



## More on Functions

First, write a function that can be looped. Note, that generally means the function works on a single vector.
```{r fun1, exercise=TRUE, exercise.lines = 5, exercise.eval=TRUE, warning=FALSE, message=FALSE}


```



## Creating a Package

```{r quiz1}
quiz(
  question("Creating a package is an easy way to keep functions at your disposal. What was the package that makes creating a package easier that we discussed in class?",
    answer("packing"),
    answer("packager"),
    answer("devtools", correct = TRUE),
    answer("creater"),
    answer("Nope.")
  ),
    question("How can you document your functions within an R script file?",
    answer("backslash"),
    answer("#'", correct = TRUE),
    answer("Just write it in"),
    answer("#*#"),
    answer("#@")
  ),
    question("What function takes the documented R script file and creates the documentation files for you?",
    answer("document()", correct = TRUE),
    answer("run()"),
    answer("It would be nice to have a function like this but no one knows how to write it."),
    answer("check()"),
    answer("create()")
  ),
    question("What files are necessary for an R package?",
    answer("DESCRIPTION", correct = TRUE),
    answer("NAMESPACE", correct = TRUE),
    answer("R folder", correct = TRUE),
    answer("man folder", correct = TRUE),
    answer("README")
  )
)
```






